\documentclass[12pt]{article}

\usepackage[english]{babel}

\begin{document}

\hfill{Zac Carlson}

\hfill{CS 311}

\hfill{Assignment \#2 Write-up}

\null

\section{Design}

\begin{itemize}
\item Implement a text mining system. Read multiple documents, finding a specific term within those documents.
\item First piece of the program is the scoring system. The scoring system is broken down into three processes. The first process reads input and parses the input into words. The second process scores the words (counts how many times the word was found in the input). The third process will output each word with its count from that specific document. 
\item The second piece of the program will search for a given term in a corpus of files. It will weigh the term frequency by the inverse document frequency by dividing number of documents by documents containing the term, and taking the log of that quotient. The output is the list of files which have the term searched for.
\item There will also be timings ased on total size and number of input files.
\end{itemize}

\section{Work Log}
\begin{itemize}

\item Given through my git log

\end{itemize}

\section{Challenges}

This whole assignment was a challenge. As I've expressed to the TA and mainly to the instructor, the time frame for this project to be done in was not good. I'm better now, but during a majority of the time working on the project, I was dealing with stress both in life and in school work. What also did not help was the snow fall that delayed school for several days during this time period. I live in a basement and I have suffered from cabin fever and am just beginning to get over it. The specific challenges from the homework were figuring out how to count the word occurences and search a file for a specific word. As you'll see, all I was able to accomplish was the parsing of the words.

\section{Questions}

\begin{itemize}
\item Point of the assignment

The point of the assignment was to reflect on what we've read in the book and what's been discussed in lecure regarding pipes and forks. We were also to reflect on our knowledge of stream functions. 

\item Ensuring the solution was correct

To ensure the solution was correct for the part I completed, I just compared what the output was to what was actually part of the file I parsed. Everything was correct, therefore the parsing part worked. 

\item What I learned

I learned how to implment pipes and forks into a program. I learned how to parse words and refreshed my memory on how to convert the text to lower case and what have you. This assignment was also a major wake up call for me. I need to get my act together and work hard on the future assignments. Yes, life outside of school and within school have made this project difficult, but I need to find a way around this in order to pass the class. 
\end{itemize}

\end{document}